---
title: "Quick Overview"
author: "Fausto Lopez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r}
library(geonyrkR)
```


This quick wrapper function gives access through R to geoclient V1. For structued addresses run the following code; to return a dataframe enter simplify = T:

```{r, echo=TRUE}

sampler = geony_raw("5123", "108st", "queens", "f2e57cb4", "68779dfdbac8b55ecbe179e6d64dd734")
sampler$address$latitude

```

In order to pull straight longitude and latitude alone run the following:

```{r, echo=TRUE}
geony_latlong("5123", "108st", "queens", "f2e57cb4", "68779dfdbac8b55ecbe179e6d64dd734")
```

For unstructured addresses run the following to get longitude and latitude:

```{r, echo=TRUE}
geony_address("314west100stmanhattan", "f2e57cb4", "68779dfdbac8b55ecbe179e6d64dd734")
```

For intersections run the following; result is a raw list, you can parse manually:

```{r, echo=TRUE}
sampler = geony_intersect("broad st","beaver st","manhattan" ,"f2e57cb4", "68779dfdbac8b55ecbe179e6d64dd734")
sampler$intersection$boroughCode1In
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
